%% =====================================================================
%% CHI 2027 FULL PAPER --- ANONYMISED REVIEW VERSION (SKELETON)
%% Official ACM single-column "manuscript" review format.
%%
%% HOW TO USE THIS FILE
%% Every section/subsection below carries a \guide{...} note in grey,
%% describing exactly what content YOU must write there. The \guide notes
%% are scaffolding only: delete each one once the real prose is written.
%% Nothing in a \guide note is a finding, quotation, statistic, or claim;
%% no data, participant material, or ethics outcome has been invented.
%% Items that depend on data you have not yet collected are marked
%% \TODO{...} so they are impossible to miss before submission.
%% =====================================================================

\documentclass[manuscript,review,anonymous]{acmart}

%% --- Review-version housekeeping -------------------------------------
\settopmatter{printacmref=false}          % no ACM ref block in review
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

\AtBeginDocument{%
  \providecommand\BibTeX{{\normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\acmConference[CHI '27]{Proceedings of the 2027 CHI Conference on Human
  Factors in Computing Systems}{April 2027}{Anonymous Location}
\acmYear{2027}
\copyrightyear{2027}
\setcopyright{none}

%% --- Author-facing scaffolding macros (remove before final) ----------
\usepackage{xcolor}
\newcommand{\guide}[1]{\par\smallskip\noindent%
  \textcolor{gray!75}{\small\textbf{[WRITE:]}\ \textit{#1}}\par\smallskip}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}

\begin{document}

%% =====================================================================
%% TITLE / AUTHORS  (anonymised)
%% =====================================================================
\title{Playing the Heatwave: Eliciting Valid Behavioural Evidence from
Disabled People for Disability-Inclusive Climate Adaptation Policy
through Location-Specific Narrative Simulation}

\guide{Title is provisional. It must foreground the THREE moves that make
this a CHI contribution rather than the ASSETS poster: (1) narrative
\emph{simulation} as a research method, (2) \emph{valid behavioural
evidence} as the object produced, (3) disability-inclusive climate
\emph{policy design and evaluation} as the application. Avoid ``game'' as
the headline noun if it makes the work read as a serious-games artefact
paper rather than a methods contribution. Consider an alternative that
names the empirical study (e.g. ``\dots: A Study with N Disabled
Participants'').}

\author{Anonymous Author(s)}
\affiliation{%
  \institution{Submission ID: \TODO{number}. Our institution (anonymised
  for review).}
  \country{}}
\renewcommand{\shortauthors}{Anonymous}

%% =====================================================================
%% ABSTRACT
%% =====================================================================
\begin{abstract}
\guide{Rewrite the abstract (150--250 words) as a \emph{complete} study,
not work-in-progress. Follow the CHI arc in 5--6 sentences: (1) Problem ---
disabled people are disproportionately harmed by climate hazards and
excluded from adaptation governance, and existing behavioural evidence is
not structured for policy design/evaluation. (2) Gap --- HCI lacks methods
that elicit \emph{valid}, decision-level behavioural evidence from
disabled people about adaptation. (3) Approach --- a location-specific,
accessible narrative simulation, grounded in literature-derived exclusion
mechanisms and co-designed with DPOs, played end-to-end through one urban
heatwave scenario. (4) Study --- the empirical study you actually run
(N participants, methods, analysis). (5) Findings --- 2--3 headline
results, including evidence bearing on the \emph{validity} question.
(6) Contribution --- method + empirical findings + design/policy
implications. Remove every phrase such as ``work in progress'',
``formative'', ``initial'', ``two participants''. Do NOT state numeric
results until they exist: mark them \TODO{} rather than inventing them.}
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003138.10003140</concept_id>
<concept_desc>Human-centered computing~Accessibility</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122</concept_id>
<concept_desc>Human-centered computing~HCI design and evaluation methods</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003123.10010860</concept_id>
<concept_desc>Human-centered computing~Empirical studies in HCI</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Human-centered computing~Accessibility}
\ccsdesc[500]{Human-centered computing~HCI design and evaluation methods}
\ccsdesc[300]{Human-centered computing~Empirical studies in HCI}

\keywords{accessibility; disability; climate adaptation; climate justice;
narrative simulation; serious games; research through design;
participatory design; behavioural evidence; policy prototyping;
disability agency; co-design}

\maketitle

%% =====================================================================
\section{Introduction}
\label{sec:intro}
%% =====================================================================
\guide{Open with the problem at policy scale: disabled people (~16\% of the
world's population) bear disproportionate climate harm produced by
inaccessible environments and exclusion from decision-making, not
impairment per se; international frameworks (CRPD, Sendai, Paris) recognise
this but recognition has not become accessible adaptation practice. Keep
this to one tight paragraph --- it is motivation, not a literature review.}

\guide{Second paragraph --- the \emph{research} gap reframed for HCI. State
the framing problem (disabled people cast as vulnerable recipients, not
agents) and then sharpen it into the gap this paper closes: rich
qualitative evidence on adaptive decision-making exists but is scattered,
non-comparable, and never structured for the decision processes where
adaptation policy is set. The HCI-specific gap: there is no method that
elicits \emph{decision-level, location-specific, behaviourally valid}
evidence \emph{from} disabled people in a form usable for adaptation policy
design and evaluation.}

\guide{Third paragraph --- the approach and why narrative \emph{simulation}.
Argue that situated, realistic, location-specific narrative simulation lets
disabled people \emph{act} within a concrete scenario rather than state
abstract preferences, surfacing trade-offs, trust, and constraints that
surveys/interviews miss. State that the simulation is (a) grounded in
literature-derived exclusion mechanisms, (b) anchored in a specific
geographic/policy context, and (c) co-designed with Disabled People's
Organisations (DPOs) so the medium does not reproduce the exclusion it
studies. Name the central empirical question: do such simulations elicit
\emph{valid} behavioural evidence?}

\guide{Fourth paragraph --- name the research questions explicitly (see
Section~\ref{sec:rqs}) and forward-reference the study. Then give the
formal contribution statement below.}

\subsection{Contributions}
\label{sec:contributions}
\guide{State 3--4 contributions as a bulleted list, each phrased as
something the paper \emph{delivers and evidences} (not promises). Suggested
shape: (1) A \emph{method} --- location-specific, accessible narrative
simulation for eliciting decision-level behavioural evidence from disabled
people, with a documented design process that traces literature-derived
exclusion mechanisms to concrete design requirements (research through
design). (2) \emph{Empirical findings} from a study with N disabled
participants on how they adapt to an urban heatwave, including the adaptive
strategies, barriers, trust, and policy preferences the simulation surfaced.
(3) \emph{Evidence on validity} --- an account of when and how in-simulation
behaviour corresponds to, and diverges from, real adaptive behaviour, and
what this means for using such evidence in policy. (4) \emph{Design and
policy implications} for disability-inclusive adaptation and for accessible
research instruments. Make explicit which contribution is the primary one
(recommend: the method + validity evidence).}

\guide{Close the introduction with one sentence positioning the paper
against the related scoping review: this paper uses the review only as
conceptual grounding; its contribution, data, and method are distinct (see
Section~\ref{sec:distinct}).}

%% =====================================================================
\section{Related Work}
\label{sec:related}
%% =====================================================================
\guide{One framing sentence: organise related work around the four pillars
the contribution sits between, and end each subsection by naming what it
leaves unresolved that this paper addresses. The review must let a reviewer
see what is already known and why this paper is new --- not a generic
survey.}

\subsection{Disability, Climate Adaptation, and the Vulnerability--Agency
Framing}
\label{sec:rw-disability}
\guide{Summarise the disability + climate-adaptation literature: dispro-
portionate harm, the vulnerability frame, and the shift toward agency,
participation, and DPO leadership. Draw on the grounding already written in
the scoping-review document (Disability/Climate/Justice; Vulnerability to
Agency; Disability Rights in Governance). End by stating the unresolved
problem: behavioural evidence on adaptive agency exists but is not
structured for design or policy use.}

\subsection{Accessibility, Disability Agency, and Participatory Design in
HCI}
\label{sec:rw-pd}
\guide{Position the work in HCI accessibility and participatory/co-design
traditions, especially work that treats disabled people as co-designers and
agents rather than test subjects, and critiques of token participation. Tie
to the design-justice / ``nothing about us without us'' literature. End by
noting that participatory accessibility work rarely targets climate
adaptation \emph{policy} evidence as its output.}

\subsection{Serious and Narrative Games, and Simulation as a Research
Method}
\label{sec:rw-games}
\guide{Two moves here. First, serious/narrative games and scenario planning
for climate education, communication, and data collection --- and their
inclusion gap (most target the general public/students; disabled people are
under-represented as players and absent as co-designers). Second, and more
important for the reframe: simulation/role-play as a \emph{research method}
in HCI and the social sciences --- what makes simulated decisions
informative, and the standing debate about the \emph{validity} of behaviour
elicited in simulated vs.\ real settings. This subsection must set up the
validity argument that Section~\ref{sec:discussion} resolves.}

\subsection{Research through Design, Policy Prototyping, and Sustainable
HCI}
\label{sec:rw-rtd}
\guide{Connect to (a) research through design as the epistemology for
producing knowledge via an artefact; (b) policy prototyping / civic and
public-sector HCI as the application frame for generating policy-relevant
evidence; (c) sustainable HCI / climate HCI as the domain. End by stating
the synthesis gap this paper fills: no prior work combines accessible
narrative simulation, RtD, and policy prototyping to produce \emph{valid
behavioural evidence from disabled people} for adaptation policy.}

\subsection{Relationship to Our Prior Scoping Review}
\label{sec:distinct}
\guide{Short, explicit subsection required by CHI's originality rule.
Tabulate or state the distinction between THIS paper and the related npj
Climate Action scoping review: different research questions (the review
asks \emph{what is known}; this paper asks \emph{how to elicit valid
behavioural evidence and what disabled people do}); different data (review =
267/42 published records; this paper = primary study data from N disabled
participants); different methods (review = bibliometrics + BERTopic +
qualitative synthesis; this paper = RtD + empirical study); different
contribution (review = synthesis of literature; this paper = a method, an
artefact, and primary findings). State that the review's exclusion
mechanisms are used here only as design \emph{input}, and no review text or
its principal contribution is reproduced.}

%% =====================================================================
\section{Research Questions}
\label{sec:rqs}
%% =====================================================================
\guide{State 2--3 RQs scoped to THIS paper (not the whole PhD). Recommended:
\textbf{RQ1} How can literature-derived mechanisms of exclusion be
translated into a location-specific, accessible narrative simulation that
elicits decision-level behavioural evidence from disabled people?
\textbf{RQ2} What does such a simulation reveal about how disabled people
adapt to a localised climate hazard (strategies, barriers, trust, policy
preferences)? \textbf{RQ3} To what extent, and under what conditions, does
the behavioural evidence it elicits appear \emph{valid} for use in
disability-inclusive adaptation policy design and evaluation? Map each RQ to
the section that answers it.}

%% =====================================================================
\section{Design of the Narrative Simulation}
\label{sec:design}
%% =====================================================================
\guide{Framing sentence: present this section as research through design ---
the artefact and its rationale are part of the contribution. Make the design
process auditable: literature-derived mechanisms $\rightarrow$ design
requirements $\rightarrow$ scenario, accessibility, and prototype.}

\subsection{Design Process and Rationale}
\label{sec:design-process}
\guide{Describe the end-to-end design process so a reviewer can assess
research quality: who was involved (research team roles, DPO partners),
the number and format of co-design activities, how decisions were made and
recorded, and how the design iterated. This is where you establish the RtD
methodology and the audit trail. Mark any not-yet-completed iterations with
\TODO{}.}

\subsection{From Exclusion Mechanisms to Design Requirements}
\label{sec:mechanisms}
\guide{Carry over the four behavioural mechanisms of exclusion from the
scoping review --- vulnerability framing, internalised acceptance of token
inclusion, DPO-led participation, institutional normalisation --- each with
its theoretical lens (social dominance / critical disability studies; system
justification; capability approach; institutional theory). Keep this brief:
it is design \emph{input}, not the paper's contribution. Then present the
translation table (below) as the bridge to requirements.}

\begin{table}[htbp]
\caption{From literature-derived exclusion mechanisms, via their theoretical
lens, to concrete narrative-simulation design requirements. (Carried over
and refined from the design rationale; ensure the caption is descriptive and
the table is screen-reader accessible --- real text, not an image.)}
\label{tab:bridge}
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}p{0.30\columnwidth}p{0.20\columnwidth}p{0.40\columnwidth}@{}}
\toprule
\textbf{Exclusion mechanism} & \textbf{Theoretical lens} & \textbf{Design requirement} \\
\midrule
Vulnerability framing & Social dominance; critical disability studies &
\emph{Framing-as-choice}: decision points where the same character can act
as protected recipient \emph{or} decision-maker, so the frame's acceptance
or contestation is observable. \\
\addlinespace
Internalised acceptance of token inclusion & System justification &
\emph{Parallel routes}: token/consultative vs.\ disabled-led decision
paths the player may accept, decline, or reconfigure. \\
\addlinespace
DPO-led participation & Capability approach &
\emph{Participation architecture as structural}: DPO-mediated channels and
twin-track communication built into the scenario, not bolted on. \\
\addlinespace
Institutional normalisation & Institutional theory &
\emph{Capability-oriented scenarios}: expose conversion factors
(information, transport, trusted intermediaries) as objects of action, not
invisible background. \\
\bottomrule
\end{tabular}
\guide{Keep the table, but add one column or sentence linking each
requirement to the RQ and to the specific decision point that operationa-
lises it, so the design is traceable end-to-end.}
\end{table}

\subsection{Selecting the Geographic and Policy Context}
\label{sec:context}
\guide{NEW section the CHI requirements demand explicitly. Justify the
choice of a specific location and policy context (e.g. the city/region whose
heat-action plan, housing stock, transport, and DPO landscape the scenario
models). Explain WHY location-specificity matters for validity: generic
scenarios elicit generic answers; realistic, locally accurate constraints
elicit behaviourally meaningful decisions. State the sources used to make
the scenario locally accurate (policy documents, climate data, accessibility
audits, DPO knowledge) and the boundaries of what the context represents.}

\subsection{Scenario Design: An Urban Heatwave}
\label{sec:scenario}
\guide{Describe the single, complete, end-to-end scenario (a wheelchair user
living alone in a top-floor flat during an urban heatwave) and its seven
linked decision points: warning information, housing conditions, transport,
healthcare, support networks, public services, DPO involvement. For each,
say which design requirement (Table~\ref{tab:bridge}) it instantiates and
what behavioural evidence it is intended to surface. Justify the single-
scenario, played-end-to-end choice (full adaptive pathway vs.\ isolated
choices). Include the scenario figure with descriptive alt text. Replace the
old poster figure that is marked ``need to revise''.}

\subsection{Accessibility Design}
\label{sec:accessibility}
\guide{Present accessibility as a design requirement, not a retrofit, and as
part of the validity argument (an inaccessible instrument cannot yield valid
evidence). Cover, concretely: input/motor (full keyboard operability, switch
access, large targets, non-pointer equivalents); timing (no time-limited
decisions; pause/save/resume); perception/comprehension (screen-reader
markup and reading order, text alternatives, contrast, plain language, no
colour-only information); and session/ethics (accessible consent; right to
pause/skip/withdraw; content screening; parallel remote option). State the
WCAG~2.2 AA target and be precise about what is \emph{implemented and tested}
vs.\ specified --- do not claim conformance you have not verified
(\TODO{conformance test status}). Note that several baselines exceed the
needs of the mobility cohort and are retained as cross-cutting benefits.}

\subsection{Prototype Implementation}
\label{sec:prototype}
\guide{Frame this as a TWO-ARTEFACT pipeline and explain why each stage
exists --- the progression is itself part of the RtD argument. Outline only;
fill the specifics (platform names, frame counts, tech stack, logged fields)
yourself.}

\subsubsection{Figma Prototype (Co-Design and Formative Testing)}
\label{sec:proto-figma}
\guide{Outline the Figma click-through artefact used for co-design with DPO
partners and formative testing: its purpose (establish narrative flow,
decision structure, and visual language; surface realism, comprehension, and
accessibility issues cheaply before engineering), which decision points it
covers, and the kind of feedback it is built to elicit. State plainly that
it does NOT implement programmatic accessibility or automated interaction
logging --- these are deferred to the web prototype --- so no validity claim
rests on it. Include a labelled Figma figure with descriptive alt text.}

\subsubsection{Programmable Web Prototype (Formal Pilot)}
\label{sec:proto-web}
\guide{Outline the engineered web prototype used for the formal pilot: that
it carries the design forward from Figma into a deployable build targeting
WCAG~2.2~AA, with real branching logic and, crucially for CHI, automated
\emph{interaction logging} (which events, choices, timings, path revisions,
and route selections are captured, and how they are stored and linked to
participant talk). This is the artefact on which the validity argument rests.
Mark anything not yet built with \TODO{} rather than describing it as done.}

%% =====================================================================
\section{Method}
\label{sec:method}
%% =====================================================================
\guide{Framing sentence naming the overall empirical design (e.g.
qualitative study with interaction logging; or mixed-methods), the unit of
analysis, and how the method answers RQ2 and RQ3. This whole section must
contain enough detail for a reviewer to judge research quality --- it cannot
read as a pilot.}

\subsection{Study Design}
\label{sec:study-design}
\guide{Outline the two-stage evaluation that mirrors the two artefacts, and
be explicit about which stage produces the paper's primary evidence. Stage 1
--- \emph{formative co-design testing} on the Figma prototype with DPO
partners and disabled participants, to refine realism, comprehension, and
accessibility (shapes the design; not the validity claim). Stage 2 --- the
\emph{formal pilot} on the programmable web prototype, where each participant
works through the simulation (walkthrough, think-aloud, post-task interview)
while interaction is logged, yielding the decision-level behavioural evidence
for RQ2 and RQ3. State session length and format (remote/in-person) and what
data each stage produces. Describe the formal pilot as the study the paper
reports, and mark uncollected parts with \TODO{}; leave N and specifics to
you.}

\subsection{Participants, Recruitment, and Inclusion Criteria}
\label{sec:participants}
\guide{Report recruitment route (DPO partner, anonymised as ``a Disabled
People's Organisation'' for review), inclusion/exclusion criteria, target N
and rationale for sample size, and the disability/access profile of the
cohort (the study scopes to mobility-related access needs for round one ---
state this and why). Provide a participant table (anonymised IDs, relevant
self-described characteristics) --- but do NOT invent demographics; mark
\TODO{participant table from collected data}. State the geographic/community
scope the sample does and does not represent.}

\subsection{Procedure}
\label{sec:procedure}
\guide{Step-by-step session protocol: consent, accessibility set-up and
checks, walkthrough, think-aloud prompts, decision points, post-task
semi-structured interview, debrief. Reference the interview guide (in
supplementary materials, anonymised). Be specific enough to reproduce.}

\subsection{Data Collection and Interaction Logging}
\label{sec:data}
\guide{Specify every data stream: audio/video or transcript of think-aloud
and interview; the interaction log (choices made, paths taken, time on
decision, revisions, use of DPO vs.\ official routes); and any artefacts. Say
how logs and talk are time-aligned for analysis. This subsection is what
lets you make the validity argument --- be concrete.}

\subsection{Analysis}
\label{sec:analysis}
\guide{Describe the analytic approach for each data type. For qualitative
talk: the coding approach (e.g. reflexive thematic analysis or grounded-
theory-informed coding), who coded, how the codebook was developed, and how
agreement/credibility was handled. For interaction logs: how choices and
paths were summarised and linked to reasoning. State the analytic question
behind RQ3: how you assess correspondence between in-simulation behaviour
and reported/known real behaviour. Reference the coding framework in
supplementary materials. Mark analysis not yet done with \TODO{}.}

\subsection{Researcher Reflexivity and Positionality}
\label{sec:reflexivity}
\guide{Required by CHI for this kind of work. State the research team's
positionality relative to disability and to the study community, how that
shaped design and interpretation, the role of DPO partners as co-designers
(not just recruiters), and steps taken to avoid speaking \emph{for}
participants. Keep it specific and honest.}

\subsection{Ethics}
\label{sec:ethics}
\guide{Write the ethics statement to this fixed structure; fill the keywords
yourself. (1) \emph{Status} --- application is currently IN PREPARATION /
under review at the authors' institution (anonymised); state this honestly
and do NOT claim approval has been granted. (2) \emph{Safeguard} --- state
that no participant data are collected or reported until the protocol is
approved, so every result in the paper falls under the approved protocol
(\TODO{update wording once approval is granted}). (3) \emph{Consent} ---
accessible, informed, ongoing; right to pause, skip, or withdraw without
penalty. (4) \emph{Privacy and data handling} --- anonymisation, storage,
retention, access. (5) \emph{Accessibility provisions} for participation
(see Section~\ref{sec:accessibility}). (6) \emph{Safeguarding} ---
distress-content screening, support routes, debrief. Keep it concise; leave
committee/institution names anonymised for review.}

\subsection{Terminology and Disability Language}
\label{sec:terminology}
\guide{Short subsection: state and justify your disability-language choices
(e.g. identity-first vs.\ person-first and why), acknowledge that
communities differ, and name which disability communities and geographic
contexts the study \emph{does} and \emph{does not} represent. This both
satisfies the inclusive-writing requirement and pre-empts a validity
critique about over-generalisation.}

%% =====================================================================
\section{Findings}
\label{sec:findings}
%% =====================================================================
\guide{This section currently does not exist in the poster and is the single
most important thing to write for a complete CHI paper. Organise findings as
2--4 themes that answer RQ2 (how disabled people adapted: strategies,
barriers, trust, policy preferences surfaced at the decision points) and at
least one theme answering RQ3 (signals of validity --- e.g. where
participants recognised the scenario as realistic, corrected it from lived
experience, or where in-simulation choices matched/diverged from what they
said they do in reality). Each theme: a claim, supporting evidence from BOTH
the interaction log and participant talk, and an illustrative anonymised
quotation. \TODO{All findings, themes, quotations, and counts must come from
collected, analysed data --- none may be written until that data exists. Do
not fabricate.} Include any figures/tables summarising choice
distributions or pathway patterns, with accessible captions.}

\subsection{\TODO{Theme 1 --- name after analysis}}
\guide{Placeholder for first finding theme. Replace title with the analysed
theme; one paragraph of claim + evidence + quote.}

\subsection{\TODO{Theme 2 --- name after analysis}}
\guide{Placeholder. As above.}

\subsection{\TODO{Theme 3 --- name after analysis (validity-bearing)}}
\guide{Placeholder for the theme that speaks to RQ3 (validity of elicited
behaviour). As above.}

%% =====================================================================
\section{Discussion}
\label{sec:discussion}
%% =====================================================================
\guide{Open by restating the contribution in light of the findings, then
organise into the subsections below. Make the HCI contribution explicit
here (originality, significance, validity).}

\subsection{Validity of Behavioural Evidence from Narrative Simulation}
\label{sec:disc-validity}
\guide{The intellectual core of the reframed paper. Argue, from the
findings, the conditions under which location-specific narrative simulation
elicits \emph{valid} behavioural evidence from disabled people --- and where
it does not. Address the standard threats (in-game vs.\ real behaviour,
demand characteristics, scenario realism, single-context specificity) and
say how the design and data mitigate or expose them. Be candid: position the
simulation as a structured elicitation method, not a predictor of conduct.
This subsection is what elevates the work from an artefact paper to a methods
contribution.}

\subsection{Design Implications for Accessible Research Instruments and
Adaptation Tools}
\label{sec:disc-design}
\guide{Generalise from the specific artefact to transferable design
implications: e.g. framing-as-choice, parallel routes, structural
participation architecture, and capability-oriented scenarios as reusable
patterns for accessible simulation/elicitation instruments beyond this
hazard and cohort.}

\subsection{Implications for Disability-Inclusive Adaptation Policy}
\label{sec:disc-policy}
\guide{Spell out how the evidence the method produces can feed adaptation
\emph{policy design and evaluation} --- the headline of the reframe. Connect
to how decision-level, comparable behavioural evidence could inform heat-
action planning, twin-track communication, and (forward-looking, clearly
labelled) computational policy evaluation, without overclaiming.}

\subsection{Limitations}
\label{sec:limitations}
\guide{State limitations plainly and proportionately: single hazard (urban
heat) and single access group (mobility) by design; specific geographic/
policy context; sample size and recruitment through one DPO; simulation--
reality gap; prototype maturity for the reported study. Frame these as
scope boundaries that define the agenda, and point to which are addressed by
the design vs.\ left for future work. Remove the old ``two participants /
work in progress'' framing.}

%% =====================================================================
\section{Conclusion}
\label{sec:conclusion}
%% =====================================================================
\guide{One paragraph. Restate the problem, the method (location-specific
accessible narrative simulation grounded in exclusion mechanisms and
co-designed with DPOs), the key findings, and the validity verdict, then the
contribution to HCI methods/design/practice. End with the most credible
single line of future work (e.g. extension to other hazards/access needs and
to computational policy evaluation) --- as an extension of a complete
contribution, NOT as the thing that completes it.}

%% =====================================================================
%% ETHICS / OPEN-SCIENCE STATEMENTS (anonymised) -- optional per venue
%% =====================================================================
\guide{If CHI 2027 requires separate ethics/open-science statements outside
the main text, place anonymised versions here. Otherwise keep ethics in
Section~\ref{sec:ethics}.}

%% =====================================================================
\bibliographystyle{ACM-Reference-Format}
\bibliography{Reference}
%% =====================================================================

\appendix
\section{Supplementary Materials (Anonymised)}
\guide{List, do not embed, the supplementary materials and confirm each is
anonymised: interview guide, scenario script, study protocol, coding
framework, prototype walkthrough, and optional prototype video. State
explicitly that the main paper's contribution is understandable without
them (CHI requirement). Ensure nothing essential (methods, results, contri-
bution claims) lives only here.}

\end{document}
